02_LH-SIP_Quantification

### 2022-11-28 02_LH-SIP_Quantification.Rmd
commented

    # Calculate uncertainty in turnover rate
    su_d = calculate_sigma_mu(
      # Mean values:
      a = a,
      F_L = f_label,
      F_T = f_t,
      F_0 = f_start,
      t = d_t,
      # Uncertainties:
      sF_0 = F_0_at2H_se,
      sF_L = F_label_se,
      sF_T = calibrated_at2H_without_memory_se,
      sa = sa
    ),

>>>>

    # Calculate uncertainty in turnover rate
    su_d = calculate_sigma_mu(
      # Mean values:
      a = a,
      F_L = f_label,
      F_T = f_t,
      F_0 = f_start,
      t = d_t,
      # Uncertainties:
      sF_0 = F_0_at2H_se, # uncertainty in IRMS measurement
      sF_L = F_label_se, # uncertainty in label strength
      sF_T = calibrated_at2H_without_memory_se, # uncertainty in FT due to memory-effect calculation
      sa = sa # uncertainty in assimilation efficiency
    ),
